\appendix

\section{Micro DRR Results}
\label{app:micro}

Tables~\ref{tab:micro-phaseA} and~\ref{tab:micro-phaseB} report micro DRR (Eq.~\ref{eq:drr-micro}), which pools diagnostic counts across samples before computing the reduction rate. Micro DRR down-weights samples with few diagnostics and up-weights samples with many, complementing the macro (per-sample mean) metric used in the main text.

\begin{table}[h]
\centering
\small
\caption{Phase A micro DRR results. $\Delta_\text{micro}$ = DRR$_\text{micro}$(precise) $-$ DRR$_\text{micro}$(generic).}
\label{tab:micro-phaseA}
\begin{tabular}{llrrrr}
\toprule
Model & Domain & $n$ & DRR$_\text{micro}$(P) & DRR$_\text{micro}$(G) & $\Delta_\text{micro}$ \\
\midrule
Qwen & SVG & 100 & 2.7\% & 16.0\% & $-$13.3\,pp \\
Qwen & Python & 49 & 67.2\% & 53.7\% & +13.5\,pp \\
Llama & SVG & 100 & 30.3\% & 36.8\% & $-$6.5\,pp \\
Llama & Python & 49 & 71.6\% & 68.7\% & +2.9\,pp \\
\bottomrule
\end{tabular}
\end{table}

All four cells show the same directional pattern as macro DRR (Table~\ref{tab:phaseA}): precise feedback improves DRR on Python but reduces it on SVG for both models. The magnitude of the Qwen SVG penalty is smaller under micro ($-$13.3\,pp vs.\ $-$19.9\,pp macro), consistent with the outlier analysis in Section~\ref{sec:results-phaseA}: the macro metric amplifies extreme per-sample values (e.g., sample~\#54), while micro aggregation dilutes them.

\begin{table}[h]
\centering
\small
\caption{Phase B micro DRR results on Python ($n = 49$ per cell). $\Delta_\text{micro}$ = precise $-$ generic.}
\label{tab:micro-phaseB}
\begin{tabular}{llrrrr}
\toprule
Model & Format & DRR$_\text{micro}$(P) & DRR$_\text{micro}$(G) & $\Delta_\text{micro}$ \\
\midrule
Qwen & NL & 67.2\% & 53.7\% & +13.5\,pp \\
Qwen & raw\_json & 58.2\% & 50.7\% & +7.5\,pp \\
Qwen & hybrid & 74.6\% & 55.2\% & +19.4\,pp \\
\midrule
Llama & NL & 71.6\% & 68.7\% & +2.9\,pp \\
Llama & raw\_json & 73.1\% & 77.6\% & $-$4.5\,pp \\
Llama & hybrid & 68.7\% & 74.6\% & $-$5.9\,pp \\
\bottomrule
\end{tabular}
\end{table}

Phase B micro results mirror the macro pattern (Table~\ref{tab:phaseB}): Qwen benefits from precise feedback across all three formats (hybrid $>$ NL $>$ raw\_json), while Llama shows a reversed pattern under structured formats (raw\_json and hybrid favour generic). The model-dependent interaction persists under both aggregation methods.

\section{Sensitivity Analysis}
\label{app:sensitivity}

The parse-error penalty (Eq.~\ref{eq:penalty}) adds a fixed offset of $+10$ to the effective diagnostic count for newly broken samples. Table~\ref{tab:sensitivity} reports both Qwen SVG precise and generic DRR$_\text{macro}$ under alternative penalty values, including penalty${}=0$ (no penalty at all). Both cells contain 3 newly broken samples each (precise: \#22, \#51, \#54; generic: \#22, \#54, \#76), so the penalty affects both conditions.

\begin{table}[h]
\centering
\small
\caption{Sensitivity of Qwen SVG DRR$_\text{macro}$ and $\Delta$ (precise$-$generic) to the parse-error penalty threshold ($n = 100$). ``excl \#54'' removes the most extreme outlier (1 diagnostic before correction, newly broken in both conditions).}
\label{tab:sensitivity}
\setlength{\tabcolsep}{5pt}
\begin{tabular}{lrrrr}
\toprule
Condition & DRR(P) & DRR(G) & $\Delta$ \\
\midrule
penalty $= 0$, all samples & 9.3\% & 30.8\% & $-$21.4\,pp \\
penalty $= 5$, all samples & 2.1\% & 22.8\% & $-$20.7\,pp \\
penalty $= 10$ (default), all & $-$3.2\% & 16.7\% & $-$19.9\,pp \\
penalty $= 20$, all samples & $-$13.8\% & 4.4\% & $-$18.1\,pp \\
\midrule
penalty $= 0$, excl \#54 & 9.4\% & 31.1\% & $-$21.7\,pp \\
penalty $= 10$, excl \#54 & 6.9\% & 27.0\% & $-$20.1\,pp \\
\bottomrule
\end{tabular}
\end{table}

The precise$-$generic gap $\Delta$ remains large and negative ($-$18.1 to $-$21.7\,pp) across \emph{all} penalty settings and with or without sample~\#54. Removing the penalty entirely (penalty${}=0$) \emph{widens} the gap from $-$19.9\,pp to $-$21.4\,pp, because the penalty penalises precise slightly more than generic (precise-only newly broken sample~\#51 has $b_i = 39$, contributing a larger penalty term). The qualitative conclusion---that generic feedback substantially outperforms precise on Qwen SVG---is robust to the penalty mechanism and is not an artifact of outlier handling. For all other Phase~A cells, the number of newly broken samples is $\leq 1$, making the penalty value inconsequential.

\section{Robustness Checks and Outlier Analysis}
\label{app:robustness}

\begin{table}[h]
\centering
\small
\caption{Robustness of precise$-$generic $\Delta$ to outlier-resistant estimators. Trim and Winsor at 5\%.}
\label{tab:robustness}
\begin{tabular}{lrrr}
\toprule
Cell & $\Delta_\text{mean}$ & $\Delta_\text{trim}$ & $\Delta_\text{winsor}$ \\
\midrule
Qwen SVG & $-$19.9\,pp & $-$24.0\,pp & $-$24.1\,pp \\
Qwen Python & +12.2\,pp & +13.3\,pp & +12.2\,pp \\
Llama SVG & $-$0.8\,pp & +7.6\,pp & +6.9\,pp \\
Llama Python & +2.7\,pp & +3.0\,pp & +2.7\,pp \\
\bottomrule
\end{tabular}
\end{table}

The Qwen Python precise advantage is stable across all three estimators (+12.2\% to +13.3\%), as is the Qwen SVG generic advantage ($-$19.9\% to $-$24.1\%). The Llama SVG $\Delta$ is sensitive to extreme values: the raw mean of $-$0.8\,pp shifts to +7.6\,pp under 5\% trimming, indicating that a small number of outlier samples dominate this cell.

\paragraph{Outlier analysis.}
The most extreme individual case is Qwen SVG sample~\#54, which has 1 diagnostic before correction but introduces a parse error after correction (newly broken), inflating its effective post-correction count to 11 via the penalty of Eq.~\ref{eq:penalty}. This yields a per-sample reduction of $-$10.0, heavily dragging Qwen SVG precise's macro mean negative. The sample's output was truncated at the 8192-token limit (token count = 8192), suggesting that the model attempted a verbose SVG rewrite that exceeded the generation budget. Such cases are characteristic of the SVG domain, where geometric code generation is inherently longer than Python snippet correction.
