\section{Related Work}

\paragraph{LLM self-correction.}
Self-Refine~\cite{madaan2023selfrefine}, Reflexion~\cite{shinn2023reflexion}, and Self-Debug~\cite{chen2024selfdebug} demonstrate that LLMs can revise outputs given feedback, but \citet{huang2024selfcorrect} and \citet{kamoi2024selfcorrectsurvey} show that without external oracles, self-correction is unreliable. \citet{olausson2024selfrepair} further establish that correction quality is bottlenecked by feedback quality. Self-Debug is closest to our work, comparing three feedback types that implicitly vary in specificity, but it simultaneously changes the feedback \emph{source} and its representation, precluding attribution to representation alone.

\paragraph{Verifier feedback for code.}
External feedback---compilers, test suites, static analyzers---is widely used to guide code generation. CodeT~\cite{chen2022codet}, AlphaCode~\cite{li2022alphacode}, and LEVER~\cite{ni2023lever} use execution or learned verification for ranking; LDB~\cite{zhong2024ldb} and MGDebugger~\cite{shi2024mgdebugger} apply step-level verification for debugging; SWE-agent~\cite{yang2024sweagent} and InterCode~\cite{yang2024intercode} embed tool feedback in agent loops; \citet{dolcetti2024feedbackcode} show that test failures and static-analysis reports both help open-source LLMs repair code. At training time, RLTF~\cite{liu2023rltf} and RLEF~\cite{gehring2024rlef} use execution feedback as reward signals. All these approaches focus on the \emph{presence} of feedback; the format is fixed by the tool and treated as given.

\paragraph{Prompt format effects.}
\citet{he2024promptformat} show that LLM performance swings by up to 40\,pp across prompt formats (plain text, Markdown, JSON, YAML), and \citet{lau2025cfpo} demonstrate that optimal format is task-dependent. Chain-of-thought~\cite{wei2022cot} and least-to-most prompting~\cite{zhou2023leasttomost} further illustrate the impact of information organization. Despite this evidence, no prior work has disentangled feedback \emph{representation} from feedback \emph{source}: \citet{dolcetti2024feedbackcode} varies the source (tests vs.\ static analysis) but not its rendering, and RLTF varies granularity at training time rather than in prompts. Our study fills this gap by fixing two deterministic verifiers and systematically varying both specificity and format as independent variables.
